\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\begin{document}

\textbf{Subproblem 4 --- One-dimensional alternating chains on exposed faces.}

\medskip
\textbf{Setup.}
Let $S\subset\mathbb{R}^2$ be a finite set of $n\ge 3$ points in convex position,
let $T\subset\mathbb{R}^2$ be a finite signed set (signs $\sigma(t)\in\{+1,-1\}$,
both values present), and define $\sigma(p)=\sum_{t\in T,\,p-t\in S}\sigma(t)$.

Assume the \textbf{extremal equality} $|\{p:\sigma(p)\neq 0\}|=n$.

Label vertices of $P=\operatorname{conv}(S)$ in cyclic order $s_1,\dots,s_n$ and let
$t_1,\dots,t_n\in T$ be the associated exposed translates from Subproblems 1--3
(which may be used without proof).
For each $i$, write $a_i=s_{i+1}-s_i$ and let
\[
  F_i \;=\; T\cap [t_i,t_{i+1}]
\]
be the set of translates lying on the exposed face of $Q=\operatorname{conv}(T)$
corresponding to edge $[s_i,s_{i+1}]$.

\medskip
\textbf{Statement.}
For each $i$ there exists a non-negative integer $m_i$ such that
\[
  F_i \;=\; \bigl\{t_i + k\,a_i : 0\le k\le m_i\bigr\},
  \qquad
  t_{i+1} = t_i + m_i\,a_i,
\]
and the signs alternate:
\[
  \sigma(t_i + k\,a_i) \;=\; (-1)^k\,\sigma(t_i)
  \qquad (0\le k\le m_i).
\]
In particular every face $F_i$ is a full arithmetic progression in direction $a_i$
with alternating signs.

\medskip
\textbf{Hint.}
Fix $i$ and work on the edge of $P+Q$ from $x_i=s_i+t_i$ to $x_{i+1}=s_{i+1}+t_{i+1}$.
By Subproblem 3, this edge has direction $a_i=s_{i+1}-s_i$ and its interior points
all cancel ($\sigma=0$) by the extremal equality.
A point $p$ on this edge with $p-t\in S$ can only have $p-t\in\{s_i,s_{i+1}\}$ (since $p$
is on the boundary of $P+Q$ and $t\in[t_i,t_{i+1}]$ by the face description).
Write $p=s_i+t+j\,a_i$ for $t\in F_i$ and $j\in\{0,1\}$.
The cancellation condition $\sigma(p)=0$ for every interior point of the edge then
forces the alternating-sign pattern and the arithmetic-progression structure.

\end{document}
