\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\begin{document}

\textbf{Subproblem 6 --- A convex quadrilateral with a two-point overlap is a parallelogram.}

\medskip
\textbf{Statement.}
Let $S = \{A,B,C,D\}\subset\mathbb{R}^2$ be the four vertices (in convex position) of a convex quadrilateral, listed in cyclic order around the boundary.
Let $v\in\mathbb{R}^2$, $v\neq 0$.  Suppose $|S\cap(S+v)| = 2$.

Prove: $S$ is the vertex set of a parallelogram, i.e.\ (after possible relabeling) $B-A = C-D$ and $C-B = D-A$ (opposite sides are parallel and equal), equivalently $A+C = B+D$ (the diagonals bisect each other).

\medskip
\textbf{Hint.}
Let $S\cap(S+v) = \{P,Q\}$ with $P\neq Q$.  Then $P\in S$ and $P-v\in S$; likewise $Q\in S$ and $Q-v\in S$.  The four points $P,Q,P-v,Q-v$ are all in $S = \{A,B,C,D\}$, hence (since $v\neq 0$) they are four distinct elements of $S$.  So $\{P,Q,P-v,Q-v\} = \{A,B,C,D\}$.

Now write the assignment as: $P = A$, $Q = B$, $P-v = C$, $Q-v = D$ (or some permutation consistent with the cyclic order).  The condition $P-v = C$ and $Q-v = D$ gives $A-C = v = B-D$, i.e.\ $A+D = B+C$... examine all permutations and show that the only one consistent with the cyclic convex order gives a parallelogram.

In detail: we have $v = P - (P-v)$ and $v = Q - (Q-v)$, so the two chords $P\to P-v$ and $Q\to Q-v$ in $S$ are parallel and equal.  In a convex polygon, two equal parallel chords force the four endpoints to be a parallelogram.  Prove this from the convexity/cyclic-order hypothesis.

\end{document}
